### 2023-11-09 manuscript/manuscript.Rmd
update the methods section to include the bug fixes in assignments version 1.0.1

The $AIS$ scores within each component were totalled and divided by half the total number of adduct and isotope combinations to give a component $AIS$ score ($AIS_c$).

@@

$$P_c = d \times AIS_c \times w$$
Where $d$ is the component degree and $w$ is the average component edge weight. 
The higher $P_c$, the more plausible the component subgraph.

>>>>

The $AIS$ scores within each component were totalled and divided by half the total number of adduct and isotope combinations to give a component $AIS$ score ($AIS_c$).
If an *m/z* feature was represented by more than one adduct and isotope combination in a component, the combination with the highest AIS score was retained.

@@

$$P_c = d \times AIS_c \times w$$
Where $d$ is the component degree and $w$ is the average absolute component edge weight. 
The higher $P_c$, the more plausible the component subgraph.
